Long groovy title goes here

### 2013-06-24 shanghai.tex
Added lots of newlines

Throughout this paper, $G$ stands for a commutative group scheme, smooth and locally of finite type over a finite field $\Fq$; we write $m : G\tightertimes G\to G$ for the multiplication morphism. We fix an algebraic closure $\bFq$ of $\Fq$ and write ${\bar G} $ for the commutative group scheme, smooth and locally of finite type over $\bFq$ obtained by base change; the multiplication morphism for ${\bar G}$ will be denoted by ${\bar m}$. Let $\Frob_{G}$ (resp. $\Frob_{G\tighttimes G}$) be the Frobenius automorphism of ${\bar G}$ (resp. ${\bar G}\tightertimes {\bar G}$).\Clifton{I'll insert a reference to SGA where Frobenius is defined for a large class of schemes over finite fields.}

@@

The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$}, is defined as follows.
A \cdef{character sheaf} on $G$ is a triple $\cs{L}\ceq (\gcs{L},\mu,F)$ where: 
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic sheaf on (the \'etale site of) ${\bar G}$, locally constant of rank $1$ on connected components of ${\bar G}$; 
\labitem{(CS.1)}{CS.1} $\mu: {\bar m}^* \gcs{L} \to  \gcs{L}\boxtimes \gcs{L}$ is an isomorphism of sheaves on ${\bar G}\tightertimes {\bar G}$ such that
\[
\xymatrix{
{\bar m}_3^*\gcs{L} \ar[rr]^{({\bar m}\times \id)^*\mu} \ar[d]_{(\id\tightertimes {\bar m})^*\mu}   &&  {\bar m}^*\gcs{L}\boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
\gcs{L} \boxtimes {\bar m}^* \gcs{L} \ar[rr] & &  \gcs{L} \boxtimes\gcs{L} \boxtimes \gcs{L}\\
}
\]
commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;
\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on ${\bar G}$ compatible with $\mu$ in the sense that 
\[
\xymatrix{
\Frob_{G\tighttimes G}^* {\bar m}^* \gcs{L} \ar[rr]^{\Frob_{G\tighttimes G}^*\mu} && \Frob_{G\tighttimes G}^*(\gcs{L}\boxtimes \gcs{L})\\
\ar@{=}[u] {\bar m}^*  \Frob_{G}^* \gcs{L} \ar[d]_{{\bar m}^* F} && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
{\bar m}^*\gcs{L} \ar[rr]^{\mu} && \gcs{L} \boxtimes\gcs{L}\\
}
\]
commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$ of constructible $\ell$-adic sheaves on ${\bar G}$ such
\[
\xymatrix{
\ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'} &\text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
\gcs{L} \ar[r]^{\varphi} & \gcs{L'} && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
}
\]
both commute.
\end{enumerate}

@@

Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$ determines a point ${\bar g}$ on ${\bar G}$ fixed by $\Frob_G$ and therefore an automorphism $F_{\bar g}$ of $\gcs{L}_{\bar g}$. Note that $\Aut_{\EE}(\gcs{L}_{\bar g}) \iso \EE^\times$, canonically (this follows from second condition appearing in the definition of character sheaves). The isomorphism $\mu : {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$ guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$, defined by $g \mapsto F_{\bar g}$, is a group homomorphism; we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank $1$ local system. More generally, trace is needed.} 
%
It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$ (pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$ if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism 
\[
\cdef{t_{G}} : \CS(G)_{/\text{iso}} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times), \qquad \text{defined by}\qquad 
\cs{L} \mapsto t^\Frob_\cs{L},
\]
from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.

@@

\begin{proof}
Let $\cs{L}$ be a character sheaf on $G$. We start by showing that ${\bar f}^*\gcs{L}$ is locally constant on connected components of ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any connected component and let $i$ be the image of $j$ under the group homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.\Clifton{Replace with a better reference, eventually.}  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$ for the restriction of $f$ to $\bar{H}^j$.  Since $\cs{L}$ is a character sheaf, $\gcs{L}$ is locally constant on the connect components of ${\bar G}$; thus, there is a finite etale covering $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$ is constant. Let $b_j : Y_j \to {\bar H}^j$ be the pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering of ${\bar H}^j$ and 
\[
b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right) = ({\bar f}\circ c_j \circ b_j)^*\gcs{L} = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
\]
Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back of a constant sheaf (along $g_j$, in this case) is a constant sheaf, it follows that $b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)$ is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has rank $1$ on connected components of ${\bar G}$, it follows that $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$. This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.

To see that $({\bar f}\tightertimes {\bar f})^* \gcs{L}$ satisfies condition \ref{CS.1} simply apply the functor $({\bar f}\tightertimes {\bar f})^*$ to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism $({\bar f}\tightertimes {\bar f})^*( \gcs{L} \boxtimes\gcs{L}) \iso  {\bar f}^*\gcs{L} \boxtimes {\bar f}^*\gcs{L}$ (a few times). Likewise, to see that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$. Then use the fact that $f$ is defined over $\Fq$, so $({\bar f}\tightertimes {\bar f})^* \Frob_{G\tighttimes G}^* \iso \Frob_{G\tighttimes G} ({\bar f}\tightertimes {\bar f})^*$, and the fact that $f$ is a morphism of group schemes, so $({\bar f}\tightertimes {\bar f})^* {\bar m}^* \iso {\bar m}^* {\bar f}^*$ (isomorphisms of functors on constructible sheaves).
%
To see that $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes {\bar f})^*\mu,{\bar f}^*F)$ defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors ${\bar f}^*$ and ${\bar f}^*\tightertimes{\bar f}^*$ to \ref{CS.3} and argue as above. It follows from the fact that sheaf hom commutes with these functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.

@@

%\input{connected-1}
% !TEX encoding = UTF-8 Unicode
%In this section we review a fundamental property of character sheaves on geometrically connected, commutative algebraic groups over $\Fq$.

@@

%\input{etale-1}
%In this section we establish a fundamental property of character sheaves on commutative etale group schemes over $\Fq$ that are geometrically finitely generated.

@@

\begin{proof}
To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EE^\times)$.
Recall the equivalence between etale group schemes over $\Fq$ and the category of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for the discrete topology on the group), given by $G \mapsto G(\bFq)$. Under this equivalence any character sheaf $\cs{L} =(\gcs{L},\mu,F)$ on $G$ corresponds to: 
\begin{enumerate}
\labitem{(cs.0)}{cs.0} an indexed set of one-dimensional $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over $G(\bFq)$; 
\labitem{(cs.1)}{cs.1} an indexed set of isomorphisms $\mu_{x,y}  \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$, for all $x,y \in G(\bFq)$, such that
\[
\xymatrix{
\gcs{L}_{x+y+z} \ar[rr]^{\mu_{x+y,z}} \ar[d]_{\mu_{x,y+z}}   &&  \gcs{L}_{x+y}\otimes \gcs{L}_{z} \ar[d]^{\mu_{x,y} \otimes \id} \\
\gcs{L}_{x} \otimes \gcs{L}_{y+z} \ar[rr]^{\id \otimes \mu_{y,z}} & &  \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}\\
}
\]
commutes, for all $x,y,z\in G(\bFq)$; and 
\labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ 
\Clifton{\textdbend There's hidden subtlety here too: maybe I should explain which Frobenius this is and how it acts. }
such that
\[
\xymatrix{
 \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}} &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
\gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}} && \gcs{L}_x \otimes\gcs{L}_y\\
}
\]
commutes, for all $x,y\in G(\bFq)$.
\end{enumerate}
Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of character sheaves on $G$ corresponds to:
\begin{enumerate}
\labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$ of linear transformations (of one-dimensional $\EE$-vector spaces), as $x$ runs over $G(\bFq)$, such that
\[
\xymatrix{
\ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)} &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
\gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
}
\]
both commute.
\end{enumerate}
It is clear that the category defined by conditions \ref{cs.0}, \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the proposition by exhibiting an isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.

@@

First, however, we show that such global sections exist.
Since $G(\bFq)$ is finitely-generated abelian, it admits a decomposition $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such that $G(\bFq)_\text{tors}$ is finite.
Let $x_1, \ldots , x_r$ be a basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let $y_1, \ldots , y_t$ be a generators for the torsion part of $G(\bFq)$ corresponding to the decomposition $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$; for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. .... \Clifton{I'll finish this later.} In this way we define a section $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that 
\begin{equation}\label{section}
\forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
\end{equation}
Under the equivalence at the beginning of this section, $s = s_\cs{L}$ corresponds to a global section of the line bundle $(\gcs{L},\mu)$.

>>>>

Throughout this paper, $G$ stands for a commutative group scheme,
smooth and locally of finite type over a finite field $\Fq$; we write
$m : G\tightertimes G\to G$ for the multiplication morphism. We fix an
algebraic closure $\bFq$ of $\Fq$ and write ${\bar G} $ for the
commutative group scheme, smooth and locally of finite type over
$\bFq$ obtained by base change; the multiplication morphism for
${\bar G}$ will be denoted by ${\bar m}$. Let $\Frob_{G}$
(resp. $\Frob_{G\tighttimes G}$) be the Frobenius automorphism of
${\bar G}$ (resp. ${\bar G}\tightertimes {\bar G}$).
\Clifton{I'll insert a reference to SGA where Frobenius is defined for
  a large class of schemes over finite fields.}

@@

The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
  sheaf on (the \'etale site of) ${\bar G}$, locally constant of rank
  $1$ on connected components of ${\bar G}$;

\labitem{(CS.1)}{CS.1} $\mu: {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$
  is an isomorphism of sheaves on ${\bar G}\tightertimes {\bar G}$ such that

  \[
  \xymatrix{
    {\bar m}_3^*\gcs{L} \ar[rr]^{({\bar m}\times \id)^*\mu} \ar[d]_{(\id\tightertimes {\bar m})^*\mu}
    &&  {\bar m}^*\gcs{L}\boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
    \gcs{L} \boxtimes {\bar m}^* \gcs{L} \ar[rr]
    &&  \gcs{L} \boxtimes\gcs{L} \boxtimes \gcs{L}\\
  }
  \]
  commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;

\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
  isomorphism of sheaves on ${\bar G}$ compatible with $\mu$ in the sense that

  \[
  \xymatrix{
    \Frob_{G\tighttimes G}^* {\bar m}^* \gcs{L} \ar[rr]^{\Frob_{G\tighttimes G}^*\mu}
    && \Frob_{G\tighttimes G}^*(\gcs{L}\boxtimes \gcs{L})\\
    \ar@{=}[u] {\bar m}^*  \Frob_{G}^* \gcs{L} \ar[d]_{{\bar m}^* F}
    && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
    {\bar m}^*\gcs{L} \ar[rr]^{\mu}
    && \gcs{L} \boxtimes\gcs{L}\\
  }
  \]
  commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on ${\bar G}$ such then
  \[
  \xymatrix{
  \ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'}
  & \text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
  \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
  && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
  }
  \]
  both commute.
\end{enumerate}

@@

Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
determines a point ${\bar g}$ on ${\bar G}$ fixed by $\Frob_G$ and
therefore an automorphism $F_{\bar g}$ of $\gcs{L}_{\bar g}$. Note
that $\Aut_{\EE}(\gcs{L}_{\bar g}) \iso \EE^\times$, canonically (this
follows from second condition appearing in the definition of character
sheaves). The isomorphism $\mu : {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$,
defined by $g \mapsto F_{\bar g}$, is a group homomorphism;
we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
  $1$ local system. More generally, trace is needed.}

It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$
(pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$
if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
\[
\cdef{t_{G}} : \CS(G)_{/\text{iso}} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times),
\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
\]
from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.

@@

\begin{proof}
  Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
  ${\bar f}^*\gcs{L}$ is locally constant on connected components of
  ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any
  connected component and let $i$ be the image of $j$ under the group
  homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by
  applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.
  \Clifton{Replace with a better reference, eventually.}
  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for
  the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$
  for the restriction of $f$ to $\bar{H}^j$.  Since $\cs{L}$
  is a character sheaf, $\gcs{L}$ is locally constant on the connect
  components of ${\bar G}$; thus, there is a finite etale covering
  $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$
  is constant. Let $b_j : Y_j \to {\bar H}^j$ be the
  pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be
  the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering
  of ${\bar H}^j$ and
  \[
  b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)
  = ({\bar f}\circ c_j \circ b_j)^*\gcs{L}
  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
  \]

  Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back
  of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
  it follows that $b_j^* \left( ({\bar f}^*\gcs{L})\vert_{{\bar H}^j}\right)$
  is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on
  ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every
  geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has
  rank $1$ on connected components of ${\bar G}$, it follows that
  $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$.
  This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.

  To see that $({\bar f}\tightertimes {\bar f})^* \gcs{L}$ satisfies
  condition \ref{CS.1} simply apply the functor $({\bar f}\tightertimes {\bar f})^*$
  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
  $({\bar f}\tightertimes {\bar f})^*(\gcs{L} \boxtimes\gcs{L}) \iso {\bar f}^*\gcs{L} \boxtimes {\bar f}^*\gcs{L}$
  (a few times). Likewise, to see that ${\bar f}^*\gcs{L}$ satisfies condition
  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
  Then use the fact that $f$ is defined over $\Fq$, so
  $({\bar f}\tightertimes {\bar f})^*\Frob_{G\tighttimes G}^* \iso \Frob_{G\tighttimes G} ({\bar f}\tightertimes {\bar f})^*$,
  and the fact that $f$ is a morphism of group schemes, so
  $({\bar f}\tightertimes {\bar f})^* {\bar m}^*\iso {\bar m}^* {\bar f}^*$
  (isomorphisms of functors on constructible sheaves).

  To see that $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes {\bar f})^*\mu,{\bar f}^*F)$
  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors ${\bar f}^*$ and
  ${\bar f}^*\tightertimes{\bar f}^*$ to \ref{CS.3} and argue as
  above. It follows from the fact that sheaf hom commutes with these
  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.

@@

%\input{connected-1}
% !TEX encoding = UTF-8 Unicode
%In this section we review a fundamental property of character
%sheaves on geometrically connected, commutative algebraic groups over $\Fq$.

@@

%\input{etale-1}
%In this section we establish a fundamental property of character
% sheaves on commutative etale group schemes over $\Fq$ that are
% geometrically finitely generated.

@@

\begin{proof}
  To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and
  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EE^\times)$.  Recall the
  equivalence between etale group schemes over $\Fq$ and the category
  of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for
  the discrete topology on the group), given by $G \mapsto G(\bFq)$.
  Under this equivalence any character sheaf $\cs{L}=(\gcs{L},\mu,F)$
  on $G$ corresponds to:
  \begin{enumerate}
  \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
    $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over
    $G(\bFq)$;

  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
    $\mu_{x,y} \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
    for all $x,y \in G(\bFq)$, such that
    \[
    \xymatrix{
      \gcs{L}_{x+y+z} \ar[rr]^{\mu_{x+y,z}} \ar[d]_{\mu_{x,y+z}}
      && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \ar[d]^{\mu_{x,y} \otimes \id} \\
      \gcs{L}_{x} \otimes \gcs{L}_{y+z} \ar[rr]^{\id \otimes \mu_{y,z}}
      && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}\\
      }
    \]
    commutes, for all $x,y,z\in G(\bFq)$; and

  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$
    \Clifton{\textdbend There's hidden subtlety here too: maybe I
      should explain which Frobenius this is and how it acts. }
    such that
    \[
    \xymatrix{
      \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}}
      &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
      \gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}}
      && \gcs{L}_x \otimes\gcs{L}_y\\
      }
    \]
    commutes, for all $x,y\in G(\bFq)$.
  \end{enumerate}
  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
  character sheaves on $G$ corresponds to:
  \begin{enumerate}
  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
    of linear transformations (of one-dimensional $\EE$-vector spaces),
    as $x$ runs over $G(\bFq)$, such that
    \[
    \xymatrix{
      \ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)}
      &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
      \gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x
      && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
      }
    \]
    both commute.
  \end{enumerate}
  It is clear that the category defined by conditions \ref{cs.0},
  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
  \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the
  proposition by exhibiting an isomorphism between
  $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.

@@

  First, however, we show that such global sections exist.  Since
  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
  $y_1, \ldots , y_t$ be a generators for the torsion part of
  $G(\bFq)$ corresponding to the decomposition
  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
  \Clifton{I'll finish this later.}
  In this way we define a section
  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that

  \begin{equation}\label{section}
    \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
  \end{equation}
  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.

  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(W_\Fq,G(\bFq)^*)$
  as follows. Recall that $\cs{L}$ also determines a family of linear transformations
  $F_x : \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
  spaces, so $F_x(s(\Frob(x)))$ is a scalar multiply of $s(x)$, for
  each $x\in G(\bFq)$; let $t_\cs{L}(\Frob)(x)$ be that scalar, so
  \begin{equation}\label{t}
    \forall x\in G(\bFq),\qquad F_{x}(s(\Frob(x)) = t_\cs{L}(\Frob)(x) s(x).
  \end{equation}
  Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
  the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
  $t_\cs{L}(\Frob)(x+y) = t_\cs{L}(\Frob)(x) \ t_\cs{L}(\Frob)(y)$,
  for all $x,y \in G(\bFq)$.
  % \Clifton{The alternative to this approach is to change the
  %   definition of character sheaves to incorporate the notion of
  %   Galois sheaves. That might not be so bad, but would add another
  %   layer of complication, which we wouldn't use profitably, expect
  %   here.}

  Now $t_\cs{L} : W_\Fq \to G(\bFq)^*$ is defined, recursively, by
  $t_\cs{L}(\Frob^n) \ceq t_\cs{L}(\Frob)\cdot \,^\Frob t_\cs{L}(\Frob^{n-1})$,
  where $\Frob$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
  to pointwise multiplication of functions. This gives
  \[
  \obj \CS(G(\bFq)) \longrightarrow Z^1(W_\Fq,G(\bFq)^*),
  \qquad \text{defined by} \qquad \cs{L} \mapsto t_\cs{L}.
  \]
